### 2019-04-04 _publications/jors/paper.tex
Fix for tkphd

\usepackage{biblatex}
\usepackage{hyperref}
\bibliography{paper}

\usepackage{graphicx}
\usepackage{hyperref}

@@

1. Wheeler, Daniel; (corresponding author) A\\
2. Keller, Trevor; A\\
3. DeWitt, Stephen J.; E\\
4. Jokisaari, Andrea M.; D\\
5. Schwen, Daniel; D\\
6. Guyer, Jonathan E.; A\\
7. Aagesen, Larry; D\\
8. Heinonen, Olle G.; B\\
9. Tonks, Michael R.; G\\
10. Voorhees, Peter W.; C\\
11. Warren, James A.; F

@@

B. Argonne National Laboratory, \\
Lemont, IL 60439 USA

C. Department of Materials Science and Engineering, \\
Northwestern University, \\
Evanston, IL 60208 USA

D. Fuel Modeling and Simulation Department, \\
Idaho National Laboratory, \\
Idaho Falls, ID 83415 USA

E. Materials Science and Engineering Department, \\
University of Michigan, \\
Ann Arbor, MI 48109 USA

F. Material Measurement Laboratory Office, \\
Material Measurement Laboratory, \\
National Institute of Standards and Technology,\\
Gaithersburg, MD 20899 USA

G. Department of Materials Science and Engineering, \\
University of Florida, \\
Gainesville, FL 32611

@@

Scientific communities struggle with the challenge of effectively and
efficiently sharing content and data. An online portal provides a
valuable space for scientific communities to discuss challenges and
collate scientific results. Examples of such portals include the
Micromagnetic Modeling Group ($\mu$MAG~\cite{mumag}), the Interatomic
Potentials Repository (IPR~\cite{ipr1, ipr2}) and on a larger scale
the NIH Genetic Sequence Database (GenBank~\cite{genbank}). In this
work, we present a description of a generic web portal that leverages
existing online services to provide a framework that may be adopted by
other small scientific communities. The first deployment of the PFHub
framework supports phase-field practitioners and code developers
participating in an effort to improve quality assurance for
phase-field codes.

>>>>

\usepackage[sorting=none]{biblatex}
\usepackage{hyperref}
\bibliography{paper}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{textcomp}

@@

1. Wheeler, Daniel; (corresponding author) A\\
2. Keller, Trevor; A\\
3. DeWitt, Stephen J.; B\\
4. Jokisaari, Andrea M.; C\\
5. Schwen, Daniel; C\\
6. Guyer, Jonathan E.; A\\
7. Aagesen, Larry; C\\
8. Heinonen, Olle G.; D\\
9. Tonks, Michael R.; E\\
10. Voorhees, Peter W.; F\\
11. Warren, James A.; G

@@

B. Materials Science and Engineering Department, \\
University of Michigan, \\
Ann Arbor, MI 48109 USA

C. Fuel Modeling and Simulation Department, \\
Idaho National Laboratory, \\
Idaho Falls, ID 83415 USA

D. Argonne National Laboratory, \\
Lemont, IL 60439 USA

E. Department of Materials Science and Engineering, \\
University of Florida, \\
Gainesville, FL 32611

F. Department of Materials Science and Engineering, \\
Northwestern University, \\
Evanston, IL 60208 USA

G. Material Measurement Laboratory Office, \\
Material Measurement Laboratory, \\
National Institute of Standards and Technology,\\
Gaithersburg, MD 20899 USA

@@

Scientific communities struggle with the challenge of effectively and
efficiently sharing content and data. An online portal provides a
valuable space for scientific communities to discuss challenges and
collate scientific results. Examples of such portals include the
Micromagnetic Modeling Group (\textmu MAG~\cite{mumag}), the Interatomic
Potentials Repository (IPR~\cite{ipr1, ipr2}) and on a larger scale
the NIH Genetic Sequence Database (GenBank~\cite{genbank}). In this
work, we present a description of a generic web portal that leverages
existing online services to provide a framework that may be adopted by
other small scientific communities. The first deployment of the PFHub
framework supports phase-field practitioners and code developers
participating in an effort to improve quality assurance for
phase-field codes.
